---
name: Eric
surname: Garcia
position: "Digital Marketer"
phone: "+1 (909) 438-8528"
www: www.linkedin.com/in/eric-a-garcia-220727191/
email: "ericgarcia@cpp.edu"
github: ""
linkedin: eric-a-garcia-220727191
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Motivated and skilled digital marketer and administrator with nearly 2 years of digital marketing experience and over 6 years of professional expertise across small businesses and corporate environments. Passionate about leveraging leadership to drive success in SEO, SEM, and content management while contributing to organizational growth and innovation.

# Technical Skills

-   **Programming & Tools:** R, SQL, RStudio, MS Word/Excel/PowerPoint, Canva, Adobe Photoshop, Acrobat

-   **Marketing & Analytics:** Google Analytics (Certified), HubSpot (Certified), SEMrush, Qualtrics, Social Media

-   **E-commerce Platforms:** Amazon Seller Central, Walmart Seller Center, eBay Seller Center

-   **Other Software:** ADP, Opera Cloud, SAGE

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "MS in Digital Marketing", "Expected 2025", "College of Business Administration", "California State Polytechnic University, Pomona",
  "BA in Sociology (Minor: Criminology)", "2022", "College of Letters, Arts, and Social Sciences", "California State Polytechnic University, Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "Aug 2024 – Present", "Durimex Inc. DBA Delta Tech Industries",
  list(
    "Designed and maintained user-friendly websites for brand support and customer experience.",
    "Implemented SEO and SEM strategies, boosting traffic and rankings.",
    "Managed Amazon, Walmart, and eBay listings to drive sales.",
    "Executed targeted email campaigns via Constant Contact."
  ),
  "Digital Marketing Specialist",

  "May 2024 – Jul 2024", "Parker Dewey",
  list(
    "Developed a strategic business plan for CPP Farm Store.",
    "Conducted competitor analysis to inform strategy.",
    "Created a 120-slide proposal to enhance conversions.",
    "Produced content on 2024 trends to guide marketing."
  ),
  "Independent Consultant, Internship",

  "Feb 2023 – Sep 2024", "LA MERE, LLC",
  list(
    "Managed marketing and admin for Super 8 Hotel in Indio.",
    "Oversaw social media and financial operations.",
    "Facilitated hotel sale and 1031 exchange.",
    "Managed two triple-net properties."
  ),
  "Marketing Support / Administration",

  "Aug 2022 – Dec 2022", "Strategic Marketing INC.",
  list(
    "Trained new account team members and supported onboarding.",
    "Provided client communication and workflow coordination."
  ),
  "Account Training Manager",

  "Aug 2020 – Aug 2022", "Amazon Sortation Center CN05",
  list("Assisted in order processing and logistics operations."),
  "Level 1 Associate",

  "Jun 2018 – May 2020", "New York Pizzeria",
  list("Delivered orders and provided customer service."),
  "Employee / Delivery Driver"
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```

# Projects

```{r}
tribble(
  ~ Description,
  "Recovered $60,000+ for La Mere, LLC from Riverside County DPSS.",
  "Recovered $30,000+ owed from hotel sale to Ayaan Pithiya, LLC.",
  "Collected $20,000+ in damages from CDPH for La Mere, LLC.",
  "Located $40,000 in escrow deposits during hotel sale.",
  "Resolved $6,000 in invoice discrepancies for La Mere, LLC."
) %>%
  brief_entries(Description)
```

# Certifications & Training

-   **Stukent** – Digital Marketing Simternship (Completed)

-   **HubSpot** – Inbound Marketing & Marketing Software Certifications

-   **SEMrush** – SEO Principles Certification

-   **Google Analytics** – Certified